---
title: "Julekalender_48"
output: html_document
date: "2022-12-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
The following study will try to get a view on the Danish julekalenderer that has been sent on the two tv-channels DR and Tv2 through time. The data is scrabed from the list on the bottom of each of these pages: (DR) https://da.wikipedia.org/wiki/B%C3%B8rnenes_U-landskalender and (Tv2) https://da.wikipedia.org/wiki/TV_2%27s_tv-julekalendere


# First I start off with finding the packages from Library I need for the analysis 
```{r}
library(rvest)
library(dplyr)
library(tidyr)
library(stringr)
library(janitor)
```

# Scrabing down DR's julekalendere
To scrabe down information I use the Google Chrome function 'SelectorGadget' 
```{r julekalender}
Julekalender <- "https://da.wikipedia.org/wiki/Tv-julekalender#Oversigter_over_tv-julekalendere"
# scrape the website
jul_html <- read_html(Julekalender)
```

#Extracting the wholetablet 
```{r scrape-rows}
whole_table <- jul_html %>% 
 html_nodes("tr") %>%
 html_text(trim = FALSE) 
head(whole_table)
```

#Separating the list 
```{r}
string <- whole_table
string <- unlist(strsplit(string, "\n"))
```

#Creating a dataframe
```{r}
jul_dataframe <- data.frame(string)
```

#Showing the dataframe in Rmd
```{r}
jul_dataframe
```

